Osa

### 2021-06-29 article/article.Rmd
outline, re-start clean base stats

---
title: "Osa"
output: html_notebook
---

@@

    -   can break down biomass by component

@@

    -   can break down by diversity index

>>>>

---
title: "Osa"
output: 
  html_notebook: 
    toc: yes
    code_folding: hide
    theme: spacelab
    fig_caption: yes
---

@@

    -   can break down biomass by component
    -   maybe system-level curve (e.g. biomas hist) + timber sp

@@

    -   can break down by diversity index
    -   compare to NMDS?

    1.  system-level curve (e.g. rank-abund) x distance [+ 1 timber sp]
